A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-02 sections/Discussion.tex
Typo

This section discusses some insights that we gained from our work and contrasts
the scoping mechanisms we have employed by those in DK's algorithm.
We also discuss a way to improve the precision of their scope tracking.
Furthermore we discuss and sketch an extension of our algorithm with
elaboration to a target calculus.

>>>>

This section discusses some insights that we gained from our work and contrasts
the scoping mechanisms we have employed with those in DK's algorithm.
We also discuss a way to improve the precision of their scope tracking.
Furthermore we discuss and sketch an extension of our algorithm with
an elaboration to a target calculus.
